Self Referencing Sequences

### 2014-10-27 draft.tex
edited iterative process section
addded some rules stuff

One possible iterative process is as follows. Let the sequence $\{s^0\}$ be 2, and let the sequence $\{s^{(i)}\}$ for $i \geq 1$ be the unique sequence that starts with 2 and is such that its block lengths, read from left to right, reproduce the sequence $\{s^{(i-1)}\}$. This gives:
\begin{align*}
\{s^{(0)}\} &= 2\\
\{s^{(1)}\} &= 2,2\\
\{s^{(2)}\} &= 2,2,1,1\\
\{s^{(3)}\} &= 2,2,1,1,2,1\\
\{s^{(4)}\} &= 2,2,1,1,2,1,2,2,1\\
&\cdots
\end{align*}
Let $s^\infty$ be the limit of this process. We claim that $s^\infty$ is the unique self-referential sequence $s(\{1,2\},2)$ generated by $\{1,2\}$ with starting number 2.
\begin{proof}
We prove this with induction. We show that if $s^{(i)}$ is a prefix of $s(\{1,2\},2)$, then $s^{(i+1)}$ is a longer prefix of $s(\{1,2\},2)$. The base case of the induction is satisfied, as $s^{(0)}$ is a prefix of $s(\{1,2\},2)$.

@@

>>>>

One possible iterative process is as follows. Let the sequence $\{s^0\}$ be 2, and let the sequence $\{s^{(i)}\}$ for $i \geq 1$ be the unique sequence that starts with 2 and is such that its block lengths, read from left to right, reproduce the sequence $\{s^{(i-1)}\}$. This gives:
\begin{align*}
\{s^{(0)}\} &= 2\\
\{s^{(1)}\} &= 2,2\\
\{s^{(2)}\} &= 2,2,1,1\\
\{s^{(3)}\} &= 2,2,1,1,2,1\\
\{s^{(4)}\} &= 2,2,1,1,2,1,2,2,1\\
&\cdots
\end{align*}
Let $s^\infty$ be the limit of this process. By limit, we mean the limit with respect to finitely many terms $s^{(i)}_j \rightarrow s^\infty_j$ as$i \rightarrow \infty$. We claim that $s^\infty$ is the unique self-referential sequence $s(\{1,2\},2)$ generated by $\{1,2\}$ with starting number 2.
\begin{proof}
We prove this with induction. We show that if $s^{(i)}$ is a prefix of $s(\{1,2\},2)$, then $s^{(i+1)}$ is a longer prefix of $s(\{1,2\},2)$. The base case of the induction is satisfied, as $s^{(0)}$ is a prefix of $s(\{1,2\},2)$.

@@

Why does this work? Well, first of all, notice that the rules are the natural applications of the self-referential sequence. Also, note that we have decided to make the rules of length 2; if we had made the self-referential rules $1 \rightarrow 1$ and $3 \rightarrow 333$, this would not have worked. In addition, we know that each block length preserves parity.

So we can ask, when can we do this? We would like to be able to simulate our original algorithm with this current one. We had established that our algorithm had a state corresponding to 
\begin{itemize}
\item current block length number
\item how many elements already written down in the block
\item which number we need to write.
\end{itemize}

In an algorithm with rules, we cannot remember anything about the previous rules. Therefore, each rule needs to encompas the block length numbers, the number of elements already written, and which number we need to write. The first condition is trivial to keep, since the rules themselves will say the block length numbers, in order to keep track of the numbers already written, each rule should be self-contained. That means that the rules should read off the block numbers. We would also need the length of the rules to be divisible by the size of the generating set. This is so that at the start of each rule, we always know which numbers to write.
